%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\Needspace{8\baselineskip}
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Advanced Master on European Union Law (LL.M)} % Degree
    {College of Europe} % Institution
    {Bruges, Belgium} % Location
    {Sept. 2017 - June. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
              \item {Beneficiary of the excellence-based ENP Scholarship}
                \item {Thesis: "Human rights clauses in the EU'S International agreements, with focus on the Association Agreements in the Eastern neighbourhood". Supervisor: M. Maresceau}
    \item {Attending intensive course “EU State Aid Law”, held by Prof. M. Merola}
      \end{cvitems}
    }
    
   \cventry
    {Full Degree in Law (JD equivalent)} % Degree
    {Università degli Studi Roma Tre} % Institution
    {Rome, Italy} % Location
    {Oct. 2009 - Sept. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Final Mark: 110/110 cum laude with special mention}
      \end{cvitems}
    }
    
    \cventry
    {Research Thesis Abroad} % Degree
    {Université Paris 1 Panthéon-Sorbonne} % Institution
    {Paris, France} % Location
    {May 2016 - July 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Thesis: Le contrôl juridictionnel sur les décisions de sanction des autorités administratives indépendantes: vers un modèle commun européen}
         \item {Supervisors: Prof. G. Rossi, Prof. E. Cardi, Prof. D. Capitant}
      \end{cvitems}
    }
    
    \cventry
    {Exchange Program} % Degree
    {Université Paris Descartes} % Institution
    {Paris, France} % Location
    {Oct. 2011 - June 2012} % Date(s)
    {
    \begin{cvitems} % Description(s) bullet points
\item {Eight exams passed with distinctioned related to EU law, International Law, Civil Law}
      \end{cvitems}
    }
    
    \cventry
    {Exchange Program} % Degree
    {University of Malta} % Institution
    {Msida, Malta} % Location
    {Sept. 2014 - Jan. 2015} % Date(s)
    {
     \begin{cvitems} % Description(s) bullet points
\item {Four exams passed with distinctioned related to EU law, Competiton Law, Commercial Law}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
