%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  %% Spire
  \cventry
  {Senior Software Engineer} % Job title
  {Spire Global} % Organization
  {Luxembourg, Luxembourg} % Location
  {Dec. 2022 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Design and development of ground side tools to handle satellite constellations;}
      \item {Development of Microservices using \textbf{FastAPI, Flask, PostgreSQL, Terraform, Docker, Kubernetes, Github CI/CD actions };}
      \item {Coordination of product development project co-funded by the European Space Agency (ESA)}
    \end{cvitems}
  }
    %% Remark AI
   \cventry
    {Lead Software Engineer} % Job title
    {Remark AI} % Organization
    {London,  United Kingdom} % Location
    {Sep. 2020 - Oct. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and development of an application for thermal scanning,
        mask wearing recognition and \textbf{face recognition} using thermal or basic network cameras;}
        \item {Development of Microservices using \textbf{Flask, FastAPI, C++, MongoDB, MySQL, GraphQL, Kafka,
        Traefik, Docker, Kubernetes, Gitlab CI/CD Pipelines deploying in AWS or on-premise installations};}
       % \item {Integration of AI Pipelines developed using \textbf{DeepStream} framework using C++, Python and Kafka;}
        \item {Migration of legacy python2 backends to python 3 and async implementations;}
        \item {Carried onboarding procedures for backend and frontend positions, provided mentoring for newcomers;}
        \item {Implemented RTSP re-streaming server using Gstreamer to stream local files to RTSP}
      \end{cvitems}
    }

    %% Amadeus
    \cventry
    {Senior Software Engineer} % Job title
    {Amadeus} % Organization
    {London,  United Kingdom} % Location
    {Sep. 2017 - Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[]{Description:
          \begin{itemize} % Description(s) of tasks/responsibilities
              \item {The company is a leading provider of IT services for the travel industry, hotels and airlines;}
              \item {I joined the department developing Amadeus Altéa Departure
              Control System (DCS), a software suite which addresses Departure Control activities and
              Customers Management, supporting the whole passenger flow from Check In to Boarding;}
              \item {My team was in
              charge of the passengers regulatory requirements, providing data to the country authorities and assisting
              passengers to bring the necessary documents for an international journey.}
            \end{itemize}}
        \item[]{Activities:
          \begin{itemize}
            \item {Design and Development of server applications using \textbf{C++ 11};}
            \item {Coordination and development of an urgent delivery of a system for interactive submission to China authorities,
            from development to production in 3 months;}
            \item {Design and development of a configuration system}
            \item {Coordination for a proof of concept to use \textbf{Drools management
            system} to develop a new application, using Java, Openshift, MongoDB;}
            \item {Mentoring of junior members and interns, giving \textbf{supervision and project planning} for dedicated projects}
          \end{itemize}}
      \end{cvitems}
    }

    % XID
    \cventry
    {Software Engineer} % Job title
    {XiD Technologies} % Organization
    {Singapore} % Location
    {Feb. 2015 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and Development of applications connecting 3rd party devices performing Face and Fingerprint recognition to
        \textbf{XiD FaaS system, integrating Hanvon, ZK, Suprema} with custom Business requirements;}
        \item {Integrated Fingerpint and RFID Security System and CCTV for \textbf{Changi Airport Terminal 5 construction}, providing
        real-time screen alerts, anti-passback, WP expiration functionalities;}
        \item {Algorithm design using MATLAB for testing and C/C++ for development.
        Main techniques used are HAAR detection, ASM and
        histogram-based scoring;}
        \item {Development of Embedded Software and Overview of Hardware Architecture for XiD Revo Face 1.0 and Design of a fully
        in-house made 1.5 version using ARM 9 based architecture, controlling LCD screen, EM, Mifare RFID readers, Custom illumination,
        Custom Camera mount;}
        \item {Moved to an architecture using purely off-the-shelf components using 3rd party RTSP network cameras, illumination and actuation.
        I designed and developed an orchestrator collecting the datastream to our Face Recognition algorithm, managing all devices and connecting to our customer database;
        the system was developed using C\#, using C\# bindings for C++ libraries;}
        \item {Design and Development of an Android based application using a custom-made device, to capture attendance and
        perform verification of employees using Fingerprint and RFID card, using Android Studio, Java, MySQL.}
      \end{cvitems}
    }

    % Enea
    \cventry
    {Control Systems Engineer Internship} % Job title
    {ENEA} % Organization
    {Rome, Italy} % Location
    {Jun. 2014 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In the context of research for Nuclear fusion technologies, the project’s
        goal was to identify and characterize the behaviour
        of a Tokamak liquid lithium limiter, using an infrared thermal
        camera. Using MATLAB and C++ a real-time tool was built to monitor
        the heat distribution on the liquid limiter. After post-processing, a
        mathematical model of the heat distribution on the limiter was defined;}
      \end{cvitems}
    }

    % App
    \cventry
    {Robotics Teacher} % Job title
    {High School Concetto Marchesi} % Organization
    {Catania, Italy} % Location
    {Mar. 2014 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching as a
        Robotics Expert to a class of 20 High School students for an afternoon class, project financed by EU PON;}
        \item {Theory lessons covering basic concepts of Robotics, Electronics, Programming, Cinematics, Control systems;}
        \item {Hands-on sessions building an auto-orientating PTZ camera using Arduino, Servomotors, light sensors and a webcam;}
        \item {Building a mobile 2 wheels robot self oriented using light sensors for obstacle avoidance;}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
